Air cargo load and route planning in pickup and delivery operations

### 2024-01-31 latex/eswa.tex
Main flow updated

\tikzset{
	mybox/.style={rectangle,
		draw,
		fill= myblue,
		rounded corners,
		minimum width=2cm,
		inner sep=5pt,
		align=left,
		minimum height=1cm
	},
	myarrow/.style={draw=black,
		fill=white,
		minimum width=0.6cm,
		single arrow
	},
	downarrow/.style={draw=black,
	fill=white,
	minimum width=0.6cm,
	single arrow
	},
	longarrow/.style={draw=none,
		shading=axis,
		left color=white,
		right color=myblue,
		minimum width=0.6cm,
		single arrow,
		anchor=east
	}
}

@@

@@

>>>>

\tikzset{
	mybox/.style={rectangle,
		draw,
		fill= myblue,
		rounded corners,
		minimum width=2cm,
		inner sep=5pt,
		align=left,
		minimum height=1cm
	},
	myarrow/.style={draw=black,
		fill=white,
		minimum width=0.6cm,
		single arrow
	},
	longarrow/.style={draw=none,
		shading=axis,
		left color=white,
		right color=myblue,
		minimum width=0.6cm,
		single arrow,
		anchor=east
	}
}

@@

		\path[->] (third) edge (fifth);

@@

\begin{figure}[htp]
	\centering
	\fbox{
		\begin{tikzpicture}
			\node [mybox] (one) { \small {\bf Input data:}\\
				\small \ \ \ {Aircraft parameters}\\
				\small \ \ \ {Airports and distances}\\
				\small \ \ \ {$scenario$ \ \ ($K$ and $L$)}\\
				\small \ \ \ {$surplus = \sum_{j=1}^{n_k} v_j$/$\sum_{i=1}^{m} V_i$ }\\
				\small \ \ \ {$tmax$ \ \ (overall runtime limit)}\\
				\small {{\bf Requirement:} $K < m$}
			};

			\node [mybox, below=0.7cm of one] (two) { \small {\bf Tours definition:}\\
				\small \ \ \ {{\bf if} $K \leq 6$}\\
				\small \ \ \ \ \ \ {$ntours = 2$ \ \ (optimal TSP solutions)}\\
				\small \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ {\it or}\\				
				\small \ \ \ \ \ \ {$ntours = K!$ \ \ (all possible tours)}\\
				\small \ \ \ {\bf else}\\
				\small \ \ \ \ \ \ {$ntours = 100$ \ \ (best tours obtained with TSP heuristic)}
			};

			\node [mybox, below=0.7cm of two] (three) { \small {\bf On each tour of the $ntours$:}\\
				\small \ \ \ {Calculation of a node-by-node solution (divide runtime according to shipment volumes)}\\
				\small \ \ \ {On each node of current tour:}\\
				\small \ \ \ \ \ \ \ {- Relocate packed contents with torque optimization}\\
				\small \ \ \ \ \ \ \ {- Predefine pallet destinations according to shipment volumes}\\
				\small \ \ \ \ \ \ \ {- Find a node solution (MIP, Shims, NMO, ACO, GRASP, TS, GA) }\\
				\small \ \ \ \ \ \ \ {- Accumulate values obtained from score, torque and cost}
			};

		\node[myarrow, rotate=-90] at ([yshift=-8pt]two.south) {\phantom{\tiny{aaa}}};
		\node[myarrow, rotate=-90] at ([yshift=-8pt]one.south) {\phantom{\tiny{aaa}}};		
		\end{tikzpicture} 
	}
	\caption{Solution process}
	\label{fig:process}
\end{figure}
